---
title: "Lab 00 - Hello IDS!"
author: "Manya"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Seyara", "Doa", "Jacob", 
           "Fola", "Ivy"),
  github_username = c("seyara-g", "doga2424", "3w3w3w", 
                      "fola.ed", "ivymowx"), 
  colour = c("blue", "red", "red", 
             "red", "pink"),
  hobby = c("piano", "music", "swimming", 
            "basketball", "dancing"),
  favourite_number = c(7, 6, 7, 6, 8)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows team data

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github_usernames", 
          y = "favourite_numbers",
          title = "team_data")
```
The text has been edited and it shows team data


### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
